### 2024-06-22 Chapter/1.tex
fix

Пусть $G$~— группа, $K$~— поле, а~$K^{\times}$~— его мультипликативная группа.
В~таком случае произвольный гомоморфизм $f \in \Hom(G, K^{\times})$ называют \textit{характером.}
Говорят, что характеры $f_1, f_2, \ldots, f_n$ \textit{линейно независимы,}
если
\[
  \forall \alpha_1, \alpha_2, \ldots, \alpha_n \in K.\ \alpha_1 f_1 + \alpha_2 f_2 + \ldots + \alpha_n f_n = 0 \Rightarrow \alpha_1 = \alpha_2 = \ldots = \alpha_n = 0.
\]

>>>>

Пусть $G$~— группа, $K$~— поле, а~$K^{\times}$~— его мультипликативная группа.
В~таком случае произвольный гомоморфизм $f \in \Hom(G, K^{\times})$ называют \textit{характером.}
Говорят, что характеры $f_1, \ldots, f_n$ \textit{линейно независимы,}
если
\[
  \forall \alpha_1, \ldots, \alpha_n \in K.\ \alpha_1 f_1 + \ldots + \alpha_n f_n = 0 \Rightarrow \alpha_1 = \ldots = \alpha_n = 0.
\]
